Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-28 article.tex
Rewrite (structured) abstract

@@

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Laser speckle contrast imaging (LSCI) is a label-free optical imaging technique that can provide quantitative blood flow data, which can be beneficial during specific neurosurgeries. Microfluidic phantoms are commonly used in the development of LSCI systems as they allow for system characterization and ease of hardware optimization. In this paper, we demonstrate that pressure-driven flow systems can be used to accurately and precisely control flow changes as small as 2\%, in comparison to the commonly used syringe pump systems that have difficulty resolving changes in flow of 5\%. Furthermore, we demonstrate that a multi-exposure speckle imaging (MESI) system is sensitive to small changes in flow and can accurately and repeatably quantify changes in flow as small as 2\%. These results indicate that for the characterization and development of LSCI, or MESI, systems, and to mitigate any concerns with the uncertainty in the actual flow-profile and not the hardware itself, pressure-based flow systems should be used with microfluidic channels.
\end{abstract}

@@

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that characterizing optical techniques with microfluidic studies requires highly-accurate flow control.

@@

\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?}} Compare results to manufacturer's spec. How to explain the syringe pump results being so far off? Accuracy +/- 0.5\%, Reproducibility +/- 0.05\%. The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty. Possibly move part of results text here instead?

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using a commercial flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error. Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.

>>>>

% Structured abstract section formatting
\newcommand{\abstractsection}[1]{
  \par\addvspace{.5\baselineskip}
  \noindent\textbf{#1: }\ignorespaces
}

@@

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}

\abstractsection{Significance}
Microfluidic phantom studies are commonly used for characterizing the performance of laser speckle contrast imaging (LSCI) and multi-exposure speckle imaging (MESI) instruments. The selection of the flow control system is critical for the reliable generation of flow during accuracy and sensitivity testing. The majority of recent LSCI studies using microfluidics used syringe pump flow control systems.

\abstractsection{Aim}
We quantified the uncertainty in flow generation for a syringe pump and a pressure-regulated flow system. We then assessed the performance of both LSCI and MESI using the pressure-regulated flow system across a range of physiologically-relevant flow speeds.

\abstractsection{Approach}
The syringe pump and pressure-regulated flow systems were evaluated during stepped flow profile experiments in a microfluidic device using an inline flow sensor. The uncertainty associated with each flow system was calculated and used to determine the reliability for LSCI instrument testing. The pressure-regulated flow system was then used to characterize the relative performance of LSCI and MESI during stepped flow profile experiments while using the inline flow sensor as reference.

\abstractsection{Results}
The pressure-regulated flow system produced much more stable and reproducible flow outputs compared to the syringe pump. The expanded uncertainty for the syringe pump was 8--20$\times$ higher than that of the pressure-regulated flow system across the tested flow speeds \textcolor{red}{(Should we use exact numbers here? If so, which flow speeds?)}. Using the pressure-regulated flow system, MESI outperformed single-exposure LSCI at all flow speeds and closely mirrored the flow sensor measurements, with average errors of 4.6\% and 15.7\%, respectively \textcolor{red}{(Include $\pm$ std too?)}.

\abstractsection{Conclusions}
Pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of flow measurement techniques with microfluidic studies. MESI offers more accurate relative flow measurements than traditional LSCI across a wide range of flow speeds.

\end{abstract}

@@

In this paper, we address two primary objectives. First, we quantify the uncertainty in flow generation for both a syringe pump and pressure-regulated flow system. By understanding the real-world uncertainty associated with each flow controller, we can design a microfluidic study to characterize the performance of optical imaging techniques that minimizes the impact of flow-related errors. Secondly, we use the pressure-regulated flow system to assess the performance of both LSCI and MESI across a range of physiologically-relevant flow speeds. Using the inline flow sensor as reference, we demonstrate the superior accuracy of relative flow measurements with MESI compared to traditional single-exposure LSCI. Such measurements would have been confounded by the large uncertainties associated with syringe pump flow generation. The results of this study indicate that highly-accurate flow controllers, such as pressure-regulated flow systems, should be used when characterizing optical imaging techniques with microfluidic studies.

@@

\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?} Compare results to manufacturer's spec. How to explain the syringe pump results being so far off? Accuracy +/- 0.5\%, Reproducibility +/- 0.05\%. The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty. Possibly move part of results text here instead?}

@@

This paper demonstrates that flow control system selection is critical for reliably generating flow for microfluidic studies. While ubiquitous in the LSCI community, syringe pumps suffer from poor stability and repeatability that limit their ability to properly characterize the flow sensitivity of optical imaging systems. We show that pressure-regulated flow systems should be used instead of syringe pumps when assessing the performance of MESI or LSCI with microfluidics. We determine that the uncertainty in flow generation with a pressure-regulated flow system is considerably less than that of a syringe pump system across a range of physiologically-relevant flow speeds. We use the pressure-regulated flow system to further demonstrate the superiority of MESI compared to traditional single-exposure LSCI. Using an inline flow sensor as reference, we show that MESI offers higher accuracy than LSCI across a wide range of flow speeds, with average errors of 4.6\% and 15.7\%, respectively. Given the large uncertainties associated with the syringe pump system, it would have been impossible to conclude that such measurements arose from an actual flow change rather than random or systematic error. Overall, these results indicate that highly accurate flow control is necessary for reliable characterization of a MESI or LSCI system.
